Methods to prioritise pop-up active transport infrastructure

### 2020-05-10 article.Rmd
Correct assertation that the Salford map is open data
The service provider specifically prohihibits re-use of data in their terms and conditions, though this may be because of the use of boilerplate language:

"Not to reproduce, duplicate, copy or re-sell any part of our site"
https://www.commonplace.is/acceptableuse

"If you print off, copy or download any part of our site in breach of these terms of use, your right to use our site will cease immediately and you must, at our option, return or destroy any copies of the materials you have made."
https://www.commonplace.is/terms

Because of the recent, localised and often ad-hoc nature of pop-up infrastructure, it is difficult to make, let alone test, hypotheses related to the research question.
Our broad hypothesis is that digital tools based on open data, such as the interactive map used to support community-level responses to COVID-19 in Salford [@salfordcitycouncil_salford_2020], illustrated in Figure 1, can lead to more effective use of resources allocated to pop-up interventions.

>>>>

Because of the recent, localised and often ad-hoc nature of pop-up infrastructure, it is difficult to make, let alone test, hypotheses related to the research question.
Our broad hypothesis is that digital tools based on open data, and crowdsourcing such as the interactive map used to support community-level responses to COVID-19 in Salford [@salfordcitycouncil_salford_2020], illustrated in Figure 1, can lead to more effective use of resources allocated to pop-up interventions.
